The Effectiveness of Strategies to Contain SARS-CoV-2: Testing, Vaccinations, and NPIs

### 2022-03-09 src/rev1_reply_comments.tex
Transfer from Google Doc new answers regarding vaccinations and pre-pandemic contact frequencies.

\begin{enumerate}
    \item They use contact-frequency from pre-pandemic diary data. Is  this truly useful if behavior of people is already changed by the fact there is a pandemic?
          \response{%
              We account for individual responses in behaviour to the pandemic through a time-variant multiplier that reduces the number of other (i.e. non-work, non-household, non-educational) contacts. The values at change points that mark policy announcements or fatigue effects are estimated. They are detailed in Section A.9.

@@

          \response{%
              We now cite our main reference for the susceptibilities for each age group also in the main text. We directly take the susceptibilities given by Davies et al. 2020, in their Extended Data Fig. 4.
              We base our assumption on infectiousness being independent of age on Jones et al. 2021. They report only slight differences in viral loads between German adults and children: ``The least infectious youngest children have 78\% (61, 94) of the peak culture probability of adults aged 45 to 55''. Furthermore, they caution that these lower numbers may be due to different sample taking - such as the usage of smaller pediatric swab devices - rather than actual lower viral loads and conclude that the differences, if existent, are likely not clinically relevant.
          }
    \item It is not accurate that the vaccines stop transmission. This has to be adapted accordingly. Also, the authors should state which vaccines they based this analysis on, as in which ones were in use in Germany at that time and how does that affect the relative transmissibility as it cannot be assumed that all vaccines will have the same effect.
          \response{%
              We talk in detail about the vaccines that were used in Germany and on which we base our analysis on in the last third of appendix A.1.
              We agree that vaccines do not stop transmission completely. We simplify the way vaccines reduce transmission risk considerably by assuming that 75\% of individuals achieve sterile immunity through a vaccination while the remaining 25\% remain fully susceptible. [Continue here]
          }
\end{enumerate}
}

>>>>

\begin{enumerate}
    \item They use contact-frequency from pre-pandemic diary data. Is  this truly useful if behavior of people is already changed by the fact there is a pandemic?
          \response{%

          Other models also use the Mossong data: OpenABM-Covid-19 model (Hinch2020), Bicher2021.

          We only use the pre-pandemic diary data as the starting point. Our policies, which include non-mandated individual behavior adjustments, then reduce contacts taking the type of contact into account and for the most part not randomly but in very specific ways. This allows us to account for behavior reactions and policy effects that target different types of contacts differently. For example, household contacts continue to take place no matter the policy environment. Work from home does not keep random individuals at home but every individual that works has a time-constant value that determines when he or she will stay home. Which share of the population stays home is taken from Google mobility data. In the education sector we do not use the Mossong data but use completely mechanistic models. This gives us confidence that we can sufficiently accurately represent the contact patterns during the pandemic and account for changes induced by the pandemic.

          Also, our excellent fit for most age groups gives us confidence that we manage to match actual meeting patterns. If we were far off for example for the number of work contacts, we would not be able to match either the infections of individuals in the working age (35-59) or of those that mostly do not work anymore (60-79).

          \textbf{Answer in case there is confusion because the other multiplier is 1 in fall 2020:}

          We account for individual responses in behaviour to the pandemic through a time-variant multiplier that reduces the number of other (i.e. non-work, non-household, non-educational) contacts. The values at change points that mark policy announcements or fatigue effects are estimated. They are detailed in Section A.9.

@@

          \response{%
              We now cite our main reference for the susceptibilities for each age group also in the main text. We directly take the susceptibilities given by Davies et al. 2020, in their Extended Data Fig. 4.
              We base our assumption on infectiousness being independent of age on Jones et al. 2021. They report only slight differences in viral loads between German adults and children: ``The least infectious youngest children have 78\% (61, 94) of the peak culture probability of adults aged 45 to 55''. Furthermore, they caution that these lower numbers may be due to different sample taking - such as the usage of smaller pediatric swab devices - rather than actual lower viral loads and conclude that the differences, if existent, are likely not clinically relevant.
          }
    \item It is not accurate that the vaccines stop transmission. This has to be adapted accordingly. Also, the authors should state which vaccines they based this analysis on, as in which ones were in use in Germany at that time and how does that affect the relative transmissibility as it cannot be assumed that all vaccines will have the same effect.
          \response{%
          We agree that vaccines do not stop transmission completely. We simplify the way vaccines reduce transmission risk considerably by assuming that 75\% of individuals achieve sterile immunity through a vaccination while the remaining 25\% remain fully susceptible. We are comfortable with this assumption for several reasons: 
          Firstly, the existing evidence supports the assumption that all four vaccines approved in the EU (Biontech/Pfizer, Moderna, AstraZeneca and Johnson&Johnson) provide similar levels of protection in the first few months after vaccination and against the Alpha variant (for details see the last third of appendix A.1), which is the only time period and variant our simulations cover.
          Secondly, given the surprisingly good performance of rapid tests we tried to err on the side of being too optimistic with our modelling of vaccine performance. This is  why we chose the perfect protection from vaccination for a large part of the population. 
          Thirdly, reinfections are not a big issue for the time period that we look at. The incidences were small and the chance of more than one exposure to Covid are negligibly small. Thus, the value added by a probabilistic model of vaccination protection is very small for the period that we cover.
          }
\end{enumerate}
}
